%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee 
% that it will correctly compile on your system if you have a non-standard  
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
\documentclass[10pt, a4paper]{article}
\usepackage{fontspec}
\usepackage{graphicx}
\usepackage{adjustbox}
\usepackage{geometry}
\usepackage{xunicode}
\usepackage{xltxtra}
\usepackage{sectsty}
\usepackage[normalem]{ulem}
\usepackage{marginnote}
\usepackage{hyperref} 
\usepackage{xcolor} 
\usepackage{enumitem}
\definecolor{MidnightBlue}{RGB}{9,40,217}
\usepackage{fontawesome5}
\usepackage{hyperref}
\usepackage{array}

% DOCUMENT LAYOUT
\geometry{
  a4paper,
  textwidth=5.5in,
  textheight=8.5in,
  marginparsep=7pt,
  marginparwidth=.6in
}
\setlength\parindent{0in}

% FONTS
\defaultfontfeatures{Mapping=tex-text}
\setromanfont[Ligatures={Common}, Numbers={OldStyle}]{Linux Libertine O}
\setmonofont[Scale=0.8]{Monaco}

% Define the natural colors for the logos
\definecolor{orcidlogocol}{HTML}{A6CE39}
\definecolor{linkedincol}{HTML}{0077B5}
\definecolor{twittercol}{HTML}{1DA1F2}
\definecolor{githubcol}{HTML}{181717}
\definecolor{websitecol}{HTML}{0077B5} % You can adjust this to your preferred website icon color
\definecolor{brown}{RGB}{204,125,80}

% CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}

% MARGIN YEARS
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\leavevmode\marginnote{\hspace{1cm}#1}}

\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\renewcommand*{\marginfont}{\scriptsize\color{gray}}
\setlength{\marginparsep}{8pt} % Space between main text and margin note
\setlength{\marginparwidth}{1in} % Width of the margin note
\reversemarginpar

% HEADINGS
\sectionfont{\mdseries\scshape\Large}
\subsectionfont{\mdseries\scshape\normalsize}
\subsubsectionfont{\mdseries\upshape\large}

% HYPERLINK COLORS
\hypersetup{
  colorlinks=true,
  linkcolor=MidnightBlue,
  filecolor=MidnightBlue,
  urlcolor=MidnightBlue,
  citecolor=MidnightBlue
}

\begin{document}

% Title Section
\noindent{\Huge\fontspec{Cardo} Aamir Sohail}\\
\bigskip

% Contact Information
\noindent
\begin{minipage}[t]{0.5\textwidth}
  \subsection*{MRC AIM PhD Student in Psychology}
  \textbf{Centre for Human Brain Health}\\
  \textbf{School of Psychology}\\
  \textbf{University of Birmingham} \\
  \textbf{Birmingham} \\
  \textbf{United Kingdom} 
  
\end{minipage}%
\begin{minipage}[t]{0.5\textwidth}
  \raggedleft
  \begin{tabular}[t]{@{}c@{ }l@{}}
    {\color{websitecol}\faGlobe} & \href{http://sohaamir.github.io}{sohaamir.github.io}\\
    {\color{orcidlogocol}\faOrcid} & \href{https://orcid.org/0009-0000-6584-4579}{0009-0000-6584-4579}\\
    {\color{twittercol}\faTwitter} & \href{http://twitter.com/AamirNSohail}{AamirNSohail}\\
    {\color{githubcol}\faGithub} & \href{http://github.com/sohaamir}{sohaamir}\\
    {\color{linkedincol}\faLinkedin} & \href{https://www.linkedin.com/in/aamir-sohail-3a42b9293/}{aamir-sohail-3a42b9293}\\
    {\color{brown}\faEnvelope} & \href{mailto:axs2210@student.bham.ac.uk}{axs2210@student.bham.ac.uk}
  \end{tabular}
\end{minipage}

\bigskip

%%\hrule
%\section*{Current work}
%• Hierarchical modeling of predictive choice\\
%• Transdiagnostic factors of social and direct learning\\

%\hrule
\section*{Education}
\noindent
\years{2023 - present}\textsc{PhD} in Psychology, University of Birmingham\\
\years{2018}\textsc{MSc} in Brain Imaging, University of Nottingham\\
\years{2016}\textsc{BSc} in Biomedical Science, Imperial College London

%%\hrule
\section*{Employment history}
\noindent
\years{2022 - 2023}University of Reading, CINN Operations Support\\
\years{2021-2022}University of Reading, CINN Assistant\\
\years{2021}University of Reading, Junior Research Fellow

%\hrule
\section*{Grants, honors \& awards}
\noindent
\years{2023}MRC AIM Doctoral Training Program, Medical Research Council / University of Birmingham (£100,000)\\
\vspace{0.5pt}\\
\years{2023}LGBT+ Inclusion Initiative Fund, University of Reading (up to £1,000)

\section*{Technical Skills}
\begin{description}[leftmargin=0pt, labelindent=0pt]
  \item[Programming Languages:] Python, R, MATLAB, bash, stan, \LaTeX{}
  \item[Neuroimaging Software:] FSL, SPM12, CONN, mricro
  \item[Online Research Services:] REDCap, SONA, Gorilla, Prolific, 10to8, Nutanix, git/GitHub
  \item[Other:] Web design (GitHub Pages, WordPress), Editing (DaVinci Resolve)
\end{description}

%-----------TEACHING-----------
\section*{Teaching}
\subsection*{University of Birmingham}
\textbf{Magnetic Resonance Imaging in Cognitive Neuroscience}  \hfill Jan 2024 -- Apr 2024 \\
Postgraduate level \\
\textit{Linux, bash scripting, neural basis of MRI/fMRI, FSL (ROI, diffusion and fMRI analysis) } \\
Module convenors: Dr Magda Chechlacz, Dr Martin Wilson, Professor Andrew Bagshaw \\
\subsection*{University of Reading}
\textbf{Introduction to Neuroscience Methods} \hfill Jan 2023 -- Apr 2023 \\
Undergraduate level \\
\textit{Brain structure/function, MR physics, psychopharmacology, neuroethics} \\
Module convenors: Professor Anastasia Christakou, Professor Bhismadev Chakrabarti  \\

%-----------OUTREACH-----------
\section*{Public Communications and Outreach}
\textbf{OHBM Mentorship Program}  \hfill 2024 \\
Mentor: Dr Marianna Kapsetaki, Mentee: Eleanor Benford \\

\textbf{CINN Work Experience Scheme}  \hfill 2023 \\
Responsible for running work experience placements for college students (7 programs ran) \\

\textbf{Reading Scholars} \\
Organized and ran sessions demonstrating MRI, EEG and TMS facilities to college students \\

%-----------PROFESSIONAL MEMBERSHIPS-----------
\section*{Professional Memberships and Affiliations}
\textbf{R Users Group - University of Birmingham}  \hfill 2023 - present \\

%-----------ORGANIZING CONFERENCES-----------
\section*{Organization of Conferences and Symposia}
\textbf{Reading Emotions 2023: Fluctuations and Change}  \\
\textit{15-16 June 2023, University of Reading} \\

\textbf{Cerebral Haemodynamics Symposium}  \\
\textit{23 July 2021, University of Reading (Online)} \\

%-----------CONFERENCE PRESENTATIONS-----------
\section*{Conference Presentations}
Rossetti, G.M.K., \textbf{The HAVEN Study Researchers.,} Lovegrove J.A., Gibbins J.M., Christakou A. (2022) \textbf{Preliminary
findings from the HAVEN Study: Investigating Haemostatic function, vessel health and neurocognitive health.}
\textit{Poster presented at Interpreting BOLD III.} Oxford, UK. \\

Rossetti, G.M.K., \textbf{Sohail, A.,} Bell, T., Christakou, A. (2021) \textbf{Differential haemodynamic responses in the human striatum
during initial and reversal learning.} \textit{Poster presented at Interpreting BOLD Taster Session.} Online. \\

Williams, B., Lee, O., Vanags, P., \textbf{Sohail, A.,} Brady, D., FitzGibbon, L., Christakou, A. \textbf{Test-retest reliability of
model parameter estimates in human reinforcement learning.} (2021) \textit{Poster presented at the Society for the Improvement 
of Psychological Sciences, 2021.} Online. \\

\textbf{Sohail, A.,} Myers J.F.M., Mick I., Clark L., Bowden-Jones H.M., Nutt D.J., Lingford-Hughes A.R., Turton S.P. (2016)
\textbf{Analysis of the reward system in Disordered Gamblers using MR and 11C-carfentanil PET.} \textit{Poster presented at the British 
Association for Psychopharmacology Summer Meeting.} Brighton, UK.


%-----------TALKS-----------
\section*{Talks}
Zhang, L., \& \textbf{Sohail, A. 'Neurocomputational and transdiagnostic components of social and direct learning'} (2024)
\textit{Neuromethods. Centre for Integrative Neuroscience and Neurodynamics, University of Reading.} \\

Jewell, S.L., \& \textbf{Sohail, A. 'Diversity and Graduate Recruitment - Imploring a Bio/Psychological Framework.'} (2023)
\textit{Neuromethods. Centre for Integrative Neuroscience and Neurodynamics, University of Reading.} \\

\textbf{Sohail, A. 'Improving Future-oriented Decisions through Metacognitive Coaching: A Proposed Study'.} (2023)
\textit{Early Career Researcher Conference 2023. School of Psychology and Clinical Language Sciences, University of Reading.} \\

Rossetti, G.M.K., \& \textbf{Sohail, A. 'Striatal Haemodynamic Modulation during Reversal Learning.'} (2021)
\textit{Neuromethods. Centre for Integrative Neuroscience and Neurodynamics, University of Reading.} \\


%-----------REFEREES-----------
\section*{Referees}
\textbf{Professor Anastasia Christakou} \\
Professor of Neuroscience \\
School of Psychology and Clinical Language Sciences \\
University of Reading \\
a.christakou[at]reading.ac.uk \\

\textbf{Dr Lei Zhang} \\
Associate Professor \\
School of Psychology \\
University of Birmingham \\
l.zhang.13[at]bham.ac.uk


%\vspace{1cm}
\vfill{}
%\hrulefill

\begin{center}
{\scriptsize  Last updated: \today\- •\- 
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
Typeset in \href{http://nitens.org/taraborelli/cvtex}{
\fontspec{Times New Roman}\XeTeX }\\
% ---- FILL IN THE FULL URL TO YOUR CV HERE
\href{http://sohaamir.github.io/cv}{http://sohaamir.github.io/cv}}
\end{center}

\end{document}
