%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

% \documentclass[letterpaper,11pt]{article}
\documentclass[a4paper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{changepage}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{fontawesome5} % For icons

\pagestyle{fancy}

\definecolor{linkcolor}{RGB}{0,0,255} % Blue color for links

% Define colors for each icon
\definecolor{linkedinblue}{rgb}{0, 0.24, 0.51} % Navy Blue for LinkedIn
\definecolor{orcidgreen}{rgb}{0.67, 0.88, 0.42} % Lime Green for ORCID
\definecolor{emailbrown}{rgb}{0.65, 0.49, 0.24} % Light Brown for Email
\definecolor{websiteblue}{rgb}{0, 0.78, 1} % Neon Blue for Website



\input{glyphtounicode}

\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor,
    breaklinks=true
}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-0pt}\item
  \begin{minipage}{\textwidth}
    \textbf{#1} \hfill #2 \\
    #3 \\
    #4
  \end{minipage}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
% change the leftmargin below if you want to change the indent on sections
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[left=-0.06in, label={}, itemsep=-5pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\begin{center}
    \textbf{\Huge \scshape AAMIR SOHAIL} \\ \vspace{8pt}
    {\large MRC AIM DTP PhD Student in Psychology} \\ \vspace{1pt}
    {\large School of Psychology, University of Birmingham} \\ \vspace{8pt}
 % Increased spacing here

% First row with ORCID and LinkedIn
\raisebox{-0.5\height}{\LARGE \textcolor{orcidgreen}{\faOrcid}}\ \href{https://orcid.org/0000-0002-6584-4579}{\raisebox{-0.5\height}{0000-0002-6584-4579}} \quad \quad
\raisebox{-0.5\height}{\LARGE \textcolor{linkedinblue}{\faLinkedin}}\ \href{https://www.linkedin.com/in/aamir-sohail-3a42b9293}{\raisebox{-0.5\height}{aamir-sohail-3a42b9293}} \\
\vspace{5pt} 
% Second row with Email and Website
\raisebox{-0.5\height}{\LARGE \textcolor{emailbrown}{\faEnvelope}}\ \href{mailto:axs2210@bham.ac.uk}{\raisebox{-0.5\height}{axs2210@student.bham.ac.uk}} \quad  \quad
\raisebox{-0.5\height}{\LARGE \textcolor{websiteblue}{\faGlobe}}\ \href{https://sohaamir.github.io}{\raisebox{-0.5\height}{https://sohaamir.github.io}}
\vspace{8pt} \\
Last updated: 14/01/2024
\end{center}

%-----------EDUCATION-----------
\section{Education}
\vspace{2.5pt}
\begin{adjustwidth}{0em}{0pt}
\textbf{Ph.D. Psychology} \hfill {Sep 2023 -- Sep 2027} \\
\emph{University of Birmingham} \\
% Centre for Human Brain Health, School of Psychology \\
% Thesis: Neurocomputational mechanisms of self-referencing in social anxiety \\
Supervisors: Dr Lei Zhang, Dr Patricia L. Lockwood
\end{adjustwidth}

\vspace{8pt} % Adjust the vertical space between entries

\begin{adjustwidth}{0em}{0pt}
\textbf{M.Sc. Brain Imaging} \hfill{Sep 2017 -- Sep 2018} \\
\emph{University of Nottingham} \\
% School of Psychology \\
% Thesis: A psychophysiological interactions analysis investigating the neuromodulatory role of the basal forebrain with the processing of unexpected events \\
Supervisors: Dr Claudia Danielmeier, Dr Jan Derrfuss
\end{adjustwidth}

\vspace{8pt}

\begin{adjustwidth}{0em}{0pt}
\textbf{B.Sc. Biomedical Science} \hfill{Sep 2013 -- Jun 2016} \\
\emph{Imperial College London} \\
% Faculty of Medicine \\
% Thesis: A psychophysiological interactions analysis investigating the neuromodulatory role of the basal forebrain with the processing of unexpected events \\
Supervisors: Professor Anne R. Lingford-Hughes, Dr Samuel P. Turton
\end{adjustwidth}



%-----------EXPERIENCE-----------
\section{Employment History}
\vspace{2pt}
  \resumeSubHeadingListStart
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
\resumeSubheading
  {CINN Operations Support}{Feb 2022 - Sep 2023}{School of Psychology and Clinical Language Sciences}{University of Reading}
\vspace{8pt} 
\resumeSubheading
  {CINN Assistant}{Oct 2021 - Feb 2022}{School of Psychology and Clinical Language Sciences}{University of Reading}
\vspace{8pt} 
\resumeSubheading
  {Junior Research Fellow}{Apr 2021 - Oct 2021}{School of Psychology and Clinical Language Sciences}{University of Reading}
\vspace{4pt} 
  \resumeSubHeadingListEnd
  
%-----------AWARDS-----------
\section{Honours and Awards}
\vspace{2pt}
\textbf{MRC AIM Doctoral Training Program} (\textasciitilde £100,000) \hfill Sep 2023 -- Sep 2027 \\
Medical Research Council/University of Birmingham \\
\vspace{8pt} 
\textbf{LGBT+ Inclusion Initiative Fund} (up to £1000) \hfill Jun 2023\\
University of Reading \textit{(co-applicant w/ Eleanor Benford)}
%-------------------------------------------

%-----------SKILLS-----------
\section{Technical Skills}
\vspace{2pt}
\begin{description}[left=0pt, font=\normalfont\bfseries]
  \item[Programming Languages:] Python, R, MATLAB, bash, stan, \LaTeX{}
  \item[Neuroimaging Software:] FSL, SPM12, CONN, mricro
  \item[Online Research Services:] REDCap, SONA, Gorilla, Prolific, 10to8, Nutanix, git/GitHub
  \item[Other:] Web design (GitHub Pages, WordPress), Editing (DaVinci Resolve)
\end{description}

%-----------TEACHING-----------
\section{Teaching}
\vspace{2pt}
\textbf{Magnetic Resonance Imaging in Cognitive Neuroscience}  \hfill Jan 2024 -- Apr 2024 \\
Postgraduate level, University of Birmingham \\
\textit{Linux, bash scripting, neural basis of MRI/fMRI, FSL (ROI, diffusion and fMRI analysis) } \\
Module convenors: Dr Magda Chechlacz, Dr Martin Wilson, Professor Andrew Bagshaw \\
\vspace{8pt}
\textbf{Introduction to Neuroscience Methods} \hfill Jan 2023 -- Apr 2023 \\
Undergraduate level, University of Reading \\
\textit{Brain structure/function, MR physics, psychopharmacology, neuroethics} \\
Module convenors: Professor Anastasia Christakou, Professor Bhismadev Chakrabarti  \\
\vspace{4pt} 

%-----------OUTREACH-----------
\section{Public communications and outreach}
\vspace{2pt}
\textbf{OHBM Mentorship Program}  \hfill 2024 \\
Mentor: Dr Marianna Kapsetaki, Mentee: Eleanor Benford \\
\vspace{8pt}
\textbf{CINN Work Experience Scheme}  \hfill 2023 \\
Responsible for running work experience placements for college students (7 programs ran) \\
\vspace{8pt}
\textbf{Reading Scholars} \\
<<<<<<< HEAD:classic_latex_cv/cv.tex
Organised and ran practical sessions demonstrating MRI, EEG and TMS facilities to college students\\
=======
Organised and ran practical sessions demonstrating MRI, EEG and TMS facilities \\
>>>>>>> origin/main:cv.tex
\vspace{4pt} 

%-----------MEMBERSHIPS-----------
\section{Professional memberships and affiliations}
\vspace{2pt}
\textbf{R Users Group - University of Birmingham}  \hfill 2023 -  \\
\vspace{8pt}

%-----------ORGANISING CONFERENCES-----------
\section{Organisation of conferences and symposia}
\vspace{2pt}
\textbf{Reading Emotions 2023: Fluctuations and Change}  \\
\textit{15-16 June 2023, University of Reading} \\
\vspace{8pt} 
\textbf{Cerebral Haemodynamics Symposium}  \\
\textit{23 July 2021, University of Reading (Online)} \\
\vspace{4pt}

%-----------CONFERENCE PRESENTATIONS-----------
\section{Conference presentations}
\vspace{2pt}
Rossetti, G.M.K., \textbf{The HAVEN Study Researchers.,} Lovegrove J.A., Gibbins J.M., Christakou A. (2022) \textbf{Preliminary
findings from the HAVEN Study: Investigating Haemostatic function, vessel health and neurocognitive health.}
\textit{Poster presented at Interpreting BOLD III.} Oxford, UK. \\
\vspace{8pt}
Rossetti, G.M.K., \textbf{Sohail, A.,} Bell, T., Christakou, A. (2021) \textbf{Differential haemodynamic responses in the human striatum
during initial and reversal learning.} \textit{Poster presented at Interpreting BOLD Taster Session.} Online. \\
\vspace{8pt}
Williams, B., Lee, O., Vanags, P., \textbf{Sohail, A.,} Brady, D., FitzGibbon, L., Christakou, A. \textbf{Test-retest reliability of
model parameter estimates in human reinforcement learning.} (2021) \textit{Poster presented at the Society for the Improvement 
of Psychological Sciences, 2021.} Online. \\
\vspace{8pt}
\textbf{Sohail, A.,} Myers J.F.M., Mick I., Clark L., Bowden-Jones H.M., Nutt D.J., Lingford-Hughes A.R., Turton S.P. (2016)
\textbf{Analysis of the reward system in Disordered Gamblers using MR and 11C-carfentanil PET.} \textit{Poster presented at the British 
Association for Psychopharmacology Summer Meeting.} Brighton, UK.
\vspace{4pt}

%-----------TALKS-----------
\section{Talks}
\vspace{2pt}
Jewell, S.L., \& \textbf{Sohail, A. 'Diversity and Graduate Recruitment - Imploring a Bio/Psychological Framework.'} (2023)
\textit{Neuromethods. Centre for Integrative Neuroscience and Neurodynamics, University of Reading.}
\vspace{8pt}

\textbf{Sohail, A. 'Improving Future-oriented Decisions through Metacognitive Coaching: A Proposed Study'.} (2023)
\textit{Early Career Researcher Conference 2023. School of Psychology and Clinical Language Sciences, University of Reading.}
\vspace{8pt}

Rossetti, G.M.K., \& \textbf{Sohail, A. 'Striatal Haemodynamic Modulation during Reversal Learning.'} (2021)
\textit{Neuromethods. Centre for Integrative Neuroscience and Neurodynamics, University of Reading.}
\vspace{4pt}

%-----------REFEREES-----------
\section{Referees}
\vspace{2pt}
\textbf{Professor Anastasia Christakou} \\
Professor of Neuroscience \\
School of Psychology and Clinical Language Sciences \\
University of Reading \\
a.christakou[at]reading.ac.uk \\
\vspace{8pt}
\textbf{Dr Lei Zhang} \\
Associate Professor \\
School of Psychology \\
University of Birmingham \\
l.zhang.13[at]bham.ac.uk




%-------------------------------------------
\end{document}
